DSSynth: An Automated Digital Controller Synthesis Tool for Physical Plants

### 2017-07-02 ase2017/paper.tex
wordings

Control theory targets the construction of reliable systems by providing
mathematical guarantees about the stability and the desired performance of
closed-loop dynamics, where outputs of discrete plant $G(z)$ are fed back
and compared to a reference signal to which a controller $C(z)$ should
steer~\cite{astrom1997computer}.  Fig.~\ref{fig:typical-control-system}
shows a typical closed-loop digital control system.
%
\begin{figure}[ht!]
\centering
\includegraphics[width=0.4\textwidth]{closedloopseries.pdf}
\caption{Typical Closed-loop Control System.}
\label{fig:typical-control-system}
\end{figure}

@@

There are various mathematical representations for control systems, e.g.,
transfer functions and state-space equations (difference or differential
equations).  Here, systems with a single input and a single output (SISO)
are considered and represented by transfer functions or state-space LTI
models.  LTI models are used to represent dynamics in several engineering
applications to support non-trivial tasks when applied to embedded \&
cyber-physical systems (e.g., robot manipulator, smart grid, power plants,
distributed robotics, and automatic pilot avionics).  The following
expression presents the general form of a discrete plant or a digital
controller based on the transfer function representation:
%
\begin{equation}
\small
\label{eq:transferfunction}
H(z)=\frac{B(z)}{A(z)}=\frac{b_{0}+b_{1}z^{-1}+...+b_{M}z^{-M}}{a_{0}+a_{1}z^{-1}+...+a_{N}z^{-N}},
\end{equation}
%
\noindent where $z^{-1}$ is called the backward-shift operator; $A(z)$ and $B(z)$ are 
the denominator and numerator polynomials; and $N$ and $M$
represent the denominator and numerator polynomials order, respectively.
%
In a state-space form, 
the behavior of a system is represented via a state evolution equation $x(n+1)$ and an instantaneous 
output equation $y(n)$, as follows:
%
\begin{equation}
\begin{split}
x(n+1) &= A x(n) + B u(n)
\\
y(n) &= C x(n) + D u(n), 
\end{split}\label{eq:ss-example}
\end{equation}

\noindent where $A$, $B$, $C$ and $D$ are matrices that fully specify the model. 
%
Controllers synthesis for LTI systems is richly studied in the
literature~\cite{mazo2010pessoa,DBLP:conf/emsoft/RavanbakhshS16,economakos2016automated};
however, there are many challenges when digital control system theory is
used, mainly due to the finite-word length (FWL) effects leading to
truncation or round-off errors~\cite{Guang2013, Istepanian2001}, time
discretization and quantization noise, which are typically introduced by
Analogue-to-Digital (ADC) and Digital-to-Analogue (DAC)
conversion~\cite{astrom1997computer}.

>>>>

Control theory targets the construction of reliable systems by providing
mathematical guarantees about the stability and the desired performance of
closed-loop dynamics, where outputs of discrete plant $G(z)$ are fed back
and compared to a reference signal towards which a controller $C(z)$ should
steer~\cite{astrom1997computer}.  Fig.~\ref{fig:typical-control-system}
depicts a typical closed-loop digital control system.

\begin{figure}[ht!]
\centering
\includegraphics[width=0.4\textwidth]{closedloopseries.pdf}
\caption{Typical Closed-loop Control System}
\label{fig:typical-control-system}
\end{figure}

@@

There are various ways to model control systems.  Two common ways to
represent the dynamics of such systems are transfer functions and
state-space equations (difference or differential equations).  In this
paper, we consider systems with a single input and a single output (SISO)
given either as transfer functions or state-space linear time-invariant
(LTI) models.  LTI models are a common sub-class, and are frequently used in
cyber-physical systems (e.g., in robotics, smart grids, power plants, and
avionics).  A discretized plant or a digital controller is, in generally,
given as follows when using a transfer function representation:
%
\begin{equation}
\small
\label{eq:transferfunction}
H(z)=\frac{B(z)}{A(z)}=\frac{b_{0}+b_{1}z^{-1}+...+b_{M}z^{-M}}{a_{0}+a_{1}z^{-1}+...+a_{N}z^{-N}},
\end{equation}
%
In this representation, $z^{-1}$ is called the backward-shift operator;
$A(z)$ and $B(z)$ are the denominator and numerator polynomials; and $N$ and
$M$ are the order of the denominator and numerator polynomials, respectively.

In a state-space form, the behavior of a system is represented via a state
evolution equation $x(n+1)$ and an instantaneous output equation $y(n)$, as
follows:
%
\begin{equation}
\begin{split}
x(n+1) &= A x(n) + B u(n)
\\
y(n) &= C x(n) + D u(n), 
\end{split}\label{eq:ss-example}
\end{equation}
%
where $A$, $B$, $C$ and $D$ are matrices that fully specify the model.

Controllers synthesis for LTI systems is richly studied in the
literature~\cite{mazo2010pessoa,DBLP:conf/emsoft/RavanbakhshS16,economakos2016automated};
however, there are many challenges when digital control system theory is
used, mainly due to the finite-word length (FWL) effects leading to
truncation or round-off errors~\cite{Guang2013, Istepanian2001}, time
discretization and quantization noise, which are typically introduced by
Analogue-to-Digital (ADC) and Digital-to-Analogue (DAC)
conversion~\cite{astrom1997computer}.
